Prediction of 2024 US election ...

### 2024-11-03 paper/paper.qmd
fixed headings

## Overview of American Electon System

@@

### What is the Electoral College {#sec-electoral-college}

@@

## States Poll Count

@@

## The Ideal Survey

### Objective

@@

### Sampling Frame

@@

### Survey Sending Process

@@

### Sampling Methodology

@@

### Survey Implementation & Question Creation

@@

### Survey Questions

Click this (link)[https://qualtricsxm7d2hxss4j.qualtrics.com/jfe/form/SV_1Tu3PT2eUEa1Op8] for the @qualtrics survey.

@@

### Potential Problems with the Methodology And Polls

>>>>

# Overview of American Electon System

@@

## What is the Electoral College {#sec-electoral-college}

@@

# States Poll Count

@@

# The Ideal Survey

## Objective

@@

## Sampling Frame

@@

## Survey Sending Process

@@

## Sampling Methodology

@@

## Survey Implementation & Question Creation

@@

## Survey Questions

Click this [link](https://qualtricsxm7d2hxss4j.qualtrics.com/jfe/form/SV_1Tu3PT2eUEa1Op8) for the @qualtrics survey.

@@

## Potential Problems with the Methodology And Polls
